Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-09 paper.tex
Add Andy Lang and JC Bradley as authors

\author{
  Noel M O'Boyle\correspondingauthor$^1$%
  \email{Noel M O'Boyle\correspondingauthor - baoilleach@gmail.com}
  \and
  Samuel E Adams$^2$%
  \email{Samuel E Adams - sea36@cam.ac.uk}
  \and
  Jonathan Alvarsson$^3$%
  \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
  \and
  Richard L Apodaca$^{14}$%
  \email{Richard L Apodaca - rapodaca@metamolecular.com}
  \and
  Igor V Filippov$^4$%
  \email{Igor V Filippov - igorf@helix.nih.gov}
  \and
  Rajarshi Guha$^4$%
  \email{Rajarshi Guha - guhar@mail.nih.gov}
  \and
  Robert Hanson$^5$%
  \email{Robert Hanson - hansonr@stolaf.edu}
  \and
  Marcus D Hanwell$^{6}$%
  \email{Marcus D Hanwell - marcus.hanwell@kitware.com}
  \and
  Geoffrey R Hutchison$^7$%
  \email{Geoffrey R Hutchison - geoffh@pitt.edu}
  \and
  Karol M Langner$^8$%
  \email{Karol M Langner - langnerkm@chem.leidenuniv.nl}
  \and
  Daniel M Lowe$^2$%
  \email{Daniel Lowe - dl387@cam.ac.uk}
  \and
  Dmitry Pavlov$^{9}$%
  \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
  \and
  Ola Spjuth$^3$%
  \email{ola.spjuth@farmbio.uu.se}
  \and
  Christoph Steinbeck$^{10}$%
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
  \and
  Adam L Tenderholt$^{11}$%
  \email{Adam L Tenderholt - adamlt82@u.washington.edu}
  \and
  Kevin J Theisen$^{12}$%
  \email{Kevin J Theisen - kevin@ichemlabs.com}
  \and
  Egon L Willighagen$^{13}$%
  \email{Egon L Willighagen - egon.willighagen@ki.se}
  \and
  Peter Murray-Rust$^2$%
  \email{Peter Murray-Rust - pm286@cam.ac.uk}
}

@@

\address{%
    \iid(1)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(2)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(3)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(4)NIH Center for Translational Therapeutics, 9800 Medical  Center Drive, Rockville, MD 20878, USA \\
    \iid(5)St. Olaf College, 1520 St. Olaf Ave., Northfield, MN 55057, USA \\
    \iid(6)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(7)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(8)Leiden Institute of Chemistry, Universiteit Leiden, Einsteinweg 55, 2333 CC Leiden, The Netherlands \\
    \iid(9)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(10)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(11)Department of Chemistry, University of Washington, Seattle, WA 98195, USA \\
    \iid(12)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA \\
    \iid(13)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden \\
    \iid(14)Metamolecular, LLC, 8070 La Jolla Shores Drive \#464, La Jolla, CA 92037, USA
}%

>>>>

\author{
  Noel M O'Boyle\correspondingauthor$^1$%
  \email{Noel M O'Boyle\correspondingauthor - baoilleach@gmail.com}
  \and
  Samuel E Adams$^2$%
  \email{Samuel E Adams - sea36@cam.ac.uk}
  \and
  Jonathan Alvarsson$^3$%
  \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
  \and
  Richard L Apodaca$^{4}$%
  \email{Richard L Apodaca - rapodaca@metamolecular.com}
  \and
  Jean-Claude Bradley$^5$%
  \email{Jean-Claude Bradley - bradlejc@drexel.edu}
  \and
  Igor V Filippov$^6$%
  \email{Igor V Filippov - igorf@helix.nih.gov}
  \and
  Rajarshi Guha$^6$%
  \email{Rajarshi Guha - guhar@mail.nih.gov}
  \and
  Robert Hanson$^7$%
  \email{Robert Hanson - hansonr@stolaf.edu}
  \and
  Marcus D Hanwell$^{8}$%
  \email{Marcus D Hanwell - marcus.hanwell@kitware.com}
  \and
  Geoffrey R Hutchison$^9$%
  \email{Geoffrey R Hutchison - geoffh@pitt.edu}
  \and
  Andrew SID Lang$^{10}$%
  \email{Andrew SID Lang - alang@oru.edu}
  \and
  Karol M Langner$^{11}$%
  \email{Karol M Langner - langnerkm@chem.leidenuniv.nl}
  \and
  Daniel M Lowe$^2$%
  \email{Daniel Lowe - dl387@cam.ac.uk}
  \and
  Dmitry Pavlov$^{12}$%
  \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
  \and
  Ola Spjuth$^3$%
  \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
  \and
  Christoph Steinbeck$^{13}$%
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
  \and
  Adam L Tenderholt$^{14}$%
  \email{Adam L Tenderholt - adamlt82@u.washington.edu}
  \and
  Kevin J Theisen$^{15}$%
  \email{Kevin J Theisen - kevin@ichemlabs.com}
  \and
  Egon L Willighagen$^{16}$%
  \email{Egon L Willighagen - egon.willighagen@ki.se}
  \and
  Peter Murray-Rust$^2$%
  \email{Peter Murray-Rust - pm286@cam.ac.uk}
}

@@

\address{%
    \iid(1)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(2)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(3)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(4)Metamolecular, LLC, 8070 La Jolla Shores Drive \#464, La Jolla, CA 92037, USA \\
    \iid(5)Department of Chemistry, Drexel University, 32nd and Chestnut streets, Philadelphia, PA 19104, USA \\
    \iid(6)NIH Center for Translational Therapeutics, 9800 Medical Center Drive, Rockville, MD 20878, USA \\
    \iid(7)St. Olaf College, 1520 St. Olaf Ave., Northfield, MN 55057, USA \\
    \iid(8)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(9)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(10)Department of Engineering, Computer Science, Physics, and Mathematics, Oral Roberts University, 7777 S. Lewis Ave. Tulsa, OK 74171, USA \\
    \iid(11)Leiden Institute of Chemistry, Universiteit Leiden, Einsteinweg 55, 2333 CC Leiden, The Netherlands \\
    \iid(12)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(13)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(14)Department of Chemistry, University of Washington, Seattle, WA 98195, USA \\
    \iid(15)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA \\
    \iid(16)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden 
}%
